\documentclass[24 pts]{article}
\usepackage{xeCJK}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{graphicx}
\graphicspath{ {images/} }
\usepackage{relsize}

\newcommand{\me}{\mathrm{e}}
\setCJKmainfont[BoldFont= Yu Mincho Demibold]{MS Mincho}
\title{コンピュータネットワーク特論レポート3	 }
\date{01-01-2016}
\author{Kwame Ackah Bohulu　1631133}
\begin{document}
\maketitle
\newpage
\paragraph{1}
When the transmitting station is sending to the receiving station, any other station that can communicate with the receiving station should not be allowed to send since this can cause a collision.\paragraph{}
a. When Station A is sending to Station B, only Station D can transfer frame since D is the only station that can't communicate with Station B.\paragraph{}
b. When Station B is sending to Station A, no other Stations can transfer frames since all stations can communicate with A.\paragraph{}
c. When Station B is sending to Station C, only Station E can transfer frames since it is the only Station that can't communicate with Station C.


\newpage
\paragraph{2}
At low load, the delay of pure ALOHA is less than that of slotted ALOHA. This is because, during low load there are fewer frames generated and sent during a specified time frame. This results in fewer collisions and retransmissions. In the case of pure ALOHA under the low load assumption, once the a frame is generated, it can be transffered immediately. In the case of slotted ALOHA under the low load assumption, once a frame is generated it can be transferred only at the beginning of a time slot. This wait introduces increases the delay for slotted ALOHA. \paragraph{}Going by the throughput approach, the throughput S for pure ALOHA and slotted ALOHA are $Ge^{-2G}$ and $Ge^{-G}$ respectively in frames per second, Where G is the number of retransmissions per given time frame. During low load, this value can be assumed to be very low. Finding the inverse of this gives a value in seconds/frame which is approximately equal to the delay. After finding the inverse it is seen that the delay of slotted ALOHA is higher than that of pure ALOHA.
\newpage
\paragraph{3}

Let B1 and B2 be the hash table for Bridge 1 and Bridge 2 respectively
a. When A sends a packet to G\\
B1\\
forward to - 2, 3, 4\\
B2\\
forward to -1, 2, 3
\paragraph{}

b. When E sends a packet to F\\
B1\\
forward to - 2, 3\\
B2\\
forward to -1, 3, 4
\paragraph{}

c.  When F sends a packet to B\\
B1\\
forward to - 2, 3,\\
B2\\
forward to -1, 4
\paragraph{}

d. When G sends a packet to C\\
B1\\
forward to - 2, 3\\
B2\\
forward to -1, 4
\paragraph{}

e. When D sends a packet to A\\
B1\\
forward to - 1\\
B2\\
forward to -4
\paragraph{}

f. When B sends a packet to F\\
B1\\
forward to - 4\\
B2\\
forward to -2


\end{document}