\documentclass[dvipdfmx]{beamer}
\newcommand{\folder}{/usr/local/share/texmf}
\input{\folder/hfiles/beamer}

\usepackage[orientation=portrait,size=a0,scale=1.4]{beamerposter}
\mode<presentation>{%
  \usetheme{Frankfurt}%
}

\renewcommand{\maketitle}{%
  \vspace*{1ex}%
  \begin{center}%
    \Huge\inserttitle\\%
    \LARGE\insertauthor\\%
    \Large\insertinstitute%
  \end{center}%
  \vspace*{-1ex}%
}

\setbeamerfont{block title}{size=\LARGE}

\title[Construction of Z-CCC]{~~~A General Construction of \\$Z$-Concatenative Complete Complementary Codes~~~}
  \author[Han \& Hashimoto]{Chenggao~Han and Takeshi~Hashimoto}
  \institute[UEC]{Graduate School of Informatics and Engineering, The University of Electro-Communications, Japan\\Email:\{hana,~hashimoto\}@ee.uec.ac.jp}
\date{}

\begin{document}
\begin{frame}{\maketitle}
  \begin{columns}
    \begin{column}{.45\textwidth}
      \begin{block}{Background}
      \begin{itemize}
        \item For (quasi-) synchronous CDMA systems, complete complementary codes (CCCs)  and zero correlation zone (ZCZ) sequences provide co-channel and multi-path interference free communications. \\
        \item Comparing with ZCZ sequences, CCC leads a CDMA system which has lower implementation complexity but is lacking in spectral efficiency in general.
        \item As a hybrid of CCC and ZCZ sequence, we proposed the Z-concatenative CCC (Z-CCC) and presented two Z-CCCs consisting of rows of the discrete Fourier transform (DFT) and Hadamard matrices.
        \item  In this work, we generalize the previous work and propose a novel construction of Z-CCCs.
	\end{itemize}
      \end{block}
      \vspace*{1ex}
      
      %%%%%%%%%
      \begin{definition}
      \begin{itemize}
      \item {\bf zero-correlation zone sequences}
      
       A sequence set (SS) with $M$ length-$L$ sequence, denoted by $(M,L)$-SS, $\bbS$ is called the {\it zero correlation zone SS} or $(M,L;Z)$-ZCZ if their periodic correlations satisfying
\[
\tilR_{\bs_m,\bs_{m'}}(\tau) = \tilR_{\bs_m,\bs_{m'}}(0)\delta(m-{m'}),~{\rm for}~|\tau| \leq Z
\]

	\item complete complementary codes
	
	A sequence family $\left(M,N,L\right)$-SF $\cC$, consisting of $M$ $(N,L)$-SSs, is called to the {\it complete complementary code} (CCC) or $(M,N,L)$-CCC if the sum of the correlation between $\bs_n^m$ and $\bs_n^{m'}$ satisfying
\begin{eqnarray*}
\cR_{\cC^m,\cC^{m'}}(\tau) = \sum_{n = 0}^{N-1}R_{\bs_n^m,\bs_n^{m'}}(\tau)\delta(m-{m'},\tau)
\label{CCCfun}
\end{eqnarray*}
for all $0 \leq m,m' < M$.

\item $Z$-concatenative complete complementary codes

If the $(M,NL)$-SS $\bbS$ generated by connecting sequences in each SS of an $(M,N,L)$-CCC $\cC$, {\it i.e.}, $\bbS = \{\bs^m\}_{m=0}^{M-1} = \{({\bf c}_n^m)_{n=0}^{N-1}\}_{m=0}^{M-1}$,  is an $(M,LN;Z)$-ZCZ, then $\cC$ is called the Z-concatenative CCC or $(M,N,L;Z)$-CCC. 
      
      \item Kronecker's product
      
      For two matrix ${\bf A}^{(0)}$ and ${\bf A}^{(1)}$ of sizes $M_0\times N_0$ and $M_1 \times N_1$, respectively, $\otimes$ denotes the Kronecker's product which yields a size $M_0M_1 \times N_0N_1$ matrix by the rule
\begin{eqnarray*}
{\bf A}^{(1)}\otimes {\bf A}^{(0)} = \left[a^{(1,m)}_{n}{\bf A}^{(0)}\right]_{m=0,n=0}^{M_1-1,N_1-1}
\end{eqnarray*}
      \end{itemize}
      \end{definition}
       \vspace*{1ex}
       
       %%%%%%%
      \begin{block}{Construction Method}
      Let
\begin{eqnarray*}
{\bf U}=\bigotimes_{k=0}^{K-1}{\bf F}_{N_k} :={\bf F}_{N_{(K-1)}}\otimes {\bf F}_{N_{(K-2)}}\otimes \cdots \otimes {\bf F}_{N_0}
\end{eqnarray*}
where $\bF_N$ stands for the $N$-dimensional DFT matrix.
      Then, the $(N,N,N)$-SF, $N = \prod_{k=0}^{K-1}N_k$, constructed by entry-wise multiplication $\odot$ as
\begin{eqnarray*}
\cC = [{\bf c}_n^m]_{m=0,n=0}^{N-1,N-1} = [{\bf u}_N^m\odot{\bf u}_N^n]_{m=0,n=0}^{N-1,N-1}
\label{CCCC}
\end{eqnarray*}
is an $(N,N,N;Z)$-CCC with $Z = (N_{K-1}-1)\prod_{k=0}^{K-2}N_k$.
      \end{block}
       \vspace*{1ex}
      
      %%%%%%
            \begin{block}{Construction efficiency}


For the bound achieving CCCs, {\it i.e.}, $(N,N,L;Z)$-CCCs, we have theoretical bound $Z \leq L-1$. Therefore, under definition of the merit figure $\eta := (Z+1)/L$, the construction efficiency of the proposed Z-CCC can be evaluated as
\begin{eqnarray*}
\eta = \frac{(N_{K-1}-1)\prod_{k=0}^{K-2}N_k+1}{\prod_{k=0}^{K-1}N_k} \approx \frac{N_{K-1}-1}{N_{K-1}}
\label{MF}
\end{eqnarray*}

There is a tradeoff relationship between merit figure and alphabet size. To achieve high merit figure, a large $N_{K-1}$ is expected at expenses of increasing alphabet size. 
      \end{block}
      
    \end{column}
    \begin{column}{.45\textwidth}
    
    \begin{example}
    Let
    \begin{eqnarray*}
{\bf U} = {\bf F}_4\otimes {\bf F}_2 = \left[
\begin{array}{c}
{\bf u}^{0} \cr
{\bf u}^{1} \cr
{\bf u}^{2} \cr
{\bf u}^{3} \cr
{\bf u}^{4} \cr
{\bf u}^{5} \cr
{\bf u}^{6} \cr
{\bf u}^{7}
\end{array}
\right]=\left[
\begin{array}{rrrrrrrr}
1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 \cr
1 & -1 & 1 & -1 & 1 & -1 & 1 & -1 \cr
1 & 1 & j & j & -1 & -1 & -j & -j \cr
1 & -1 & j & -j & -1 & 1 & -j & j \cr
1 & 1 & -1 & -1 & 1 & 1 & -1 & -1 \cr
1 & -1 & -1 & 1 & 1 & -1 & -1 & 1 \cr
1 & 1 & -j & -j & -1 & -1 & j & j \cr
1 & -1 & -j & j & -1 & 1 & j & -j
\end{array}
\right]
\end{eqnarray*}

Then, from the table
\begin{table}[htdp]
\caption{Parameters of the considering CCs}
\begin{center}
\begin{tabular}{c|cccccccc}
\hline
${\bf j}$ $\cdot$ ${\bf i}$ & $(00)$  & $(10)$ & $(01)$ & $(11)$ & $(02)$ & $(12)$ & $(03)$ & $(13)$ \\ \hline
$(00)$ & $(00)$  & $(10)$ & $(01)$ & $(11)$ & $(02)$ & $(12)$ & $(03)$ & $(13)$ \\
$(10)$ & $(10)$  & $(00)$ & $(11)$ & $(01)$ & $(12)$ & $(02)$ & $(13)$ & $(03)$ \\
$(01)$ & $(01)$  & $(11)$ & $(02)$ & $(12)$ & $(03)$ & $(13)$ & $(00)$ & $(10)$ \\
$(11)$ & $(11)$  & $(01)$ & $(12)$ & $(02)$ & $(13)$ & $(03)$ & $(10)$ & $(00)$ \\
$(02)$ & $(02)$  & $(12)$ & $(03)$ & $(13)$ & $(00)$ & $(10)$ & $(01)$ & $(11)$ \\
$(12)$ & $(12)$  & $(02)$ & $(13)$ & $(03)$ & $(10)$ & $(00)$ & $(11)$ & $(01)$ \\
$(03)$ & $(03)$  & $(13)$ & $(00)$ & $(10)$ & $(01)$ & $(11)$ & $(02)$ & $(12)$ \\
$(13)$ & $(13)$  & $(03)$ & $(10)$ & $(00)$ & $(11)$ & $(01)$ & $(12)$ & $(02)$ \\ \hline
 \end{tabular}
\end{center}
\label{CCTable}
\end{table}% 



the resulted SF is given by
 \begin{eqnarray*}
\mathcal{C} &=&\left[
 \begin{array}{cccccccc}
{\bf u}^{0} & {\bf u}^{1} & {\bf u}^{2} & {\bf u}^{3} & {\bf u}^{4} & {\bf u}^{5} & {\bf u}^{6} & {\bf u}^{7} \cr
{\bf u}^{1} & {\bf u}^{0} & {\bf u}^{3} & {\bf u}^{2} & {\bf u}^{5} & {\bf u}^{4} & {\bf u}^{7} & {\bf u}^{6} \cr
{\bf u}^{2} & {\bf u}^{3} & {\bf u}^{4} & {\bf u}^{5} & {\bf u}^{6} & {\bf u}^{7} & {\bf u}^{0} & {\bf u}^{1} \cr
{\bf u}^{3} & {\bf u}^{2} & {\bf u}^{5} & {\bf u}^{4} & {\bf u}^{7} & {\bf u}^{6} &  {\bf u}^{1} & {\bf u}^{0} \cr
{\bf u}^{4} & {\bf u}^{5} & {\bf u}^{6} & {\bf u}^{7} & {\bf u}^{0} & {\bf u}^{1} & {\bf u}^{2} & {\bf u}^{3} \cr
{\bf u}^{5} & {\bf u}^{4} & {\bf u}^{7} & {\bf u}^{6} & {\bf u}^{1} & {\bf u}^{0} & {\bf u}^{3} & {\bf u}^{2} \cr
{\bf u}^{6} & {\bf u}^{7} & {\bf u}^{0} & {\bf u}^{1} & {\bf u}^{2} & {\bf u}^{3} & {\bf u}^{4} & {\bf u}^{5} \cr
{\bf u}^{7} & {\bf u}^{6} & {\bf u}^{1} & {\bf u}^{0} & {\bf u}^{3} & {\bf u}^{2} & {\bf u}^{5} & {\bf u}^{4}  \end{array}
\right]
\label{CCC22}
\end{eqnarray*}

One can confirm that ${\cal C}$ is $(8,8,8)$-CCC and if we let
\begin{eqnarray*}
\mathbb{S} = \left[
\begin{array}{c}
{\bf s}^{0} \cr
{\bf s}^{1} \cr
{\bf s}^{2} \cr
{\bf s}^{3} \cr
{\bf s}^{4} \cr
{\bf s}^{5} \cr
{\bf s}^{6} \cr
{\bf s}^{7}
\end{array}
\right] = 
\left[
 \begin{array}{c}
\left({\bf u}^{0} ~ {\bf u}^{1} ~ {\bf u}^{2} ~ {\bf u}^{3} ~ {\bf u}^{4} ~ {\bf u}^{5} ~ {\bf u}^{6} ~ {\bf u}^{7} \right) \cr
\left({\bf u}^{1} ~ {\bf u}^{0} ~ {\bf u}^{3} ~ {\bf u}^{2} ~ {\bf u}^{5} ~ {\bf u}^{4} ~ {\bf u}^{7} ~ {\bf u}^{6} \right)\cr
\left({\bf u}^{2} ~ {\bf u}^{3} ~ {\bf u}^{4} ~ {\bf u}^{5} ~ {\bf u}^{6} ~ {\bf u}^{7} ~ {\bf u}^{0} ~ {\bf u}^{1} \right)\cr
\left({\bf u}^{3} ~ {\bf u}^{2} ~ {\bf u}^{5} ~ {\bf u}^{4} ~ {\bf u}^{7} ~ {\bf u}^{6} ~  {\bf u}^{1} ~ {\bf u}^{0} \right)\cr
\left({\bf u}^{4} ~ {\bf u}^{5} ~ {\bf u}^{6} ~ {\bf u}^{7} ~ {\bf u}^{0} ~ {\bf u}^{1} ~ {\bf u}^{2} ~ {\bf u}^{3} \right)\cr
\left({\bf u}^{5} ~ {\bf u}^{4} ~ {\bf u}^{7} ~ {\bf u}^{6} ~ {\bf u}^{1} ~ {\bf u}^{0} ~ {\bf u}^{3} ~ {\bf u}^{2} \right)\cr
\left({\bf u}^{6} ~ {\bf u}^{7} ~ {\bf u}^{0} ~ {\bf u}^{1} ~ {\bf u}^{2} ~ {\bf u}^{3} ~ {\bf u}^{4} ~ {\bf u}^{5} \right)\cr
\left({\bf u}^{7} ~ {\bf u}^{6} ~ {\bf u}^{1} ~ {\bf u}^{0} ~ {\bf u}^{3} ~ {\bf u}^{2} ~ {\bf u}^{5} ~ {\bf u}^{4}  \right)
\end{array}
\right]
\end{eqnarray*}
Then, it is an $(8,64; 6)$-ZCZ which merit factor is $\eta = 7/8$.
    \end{example}
      
       \vspace*{5ex}
      
      
      \begin{block}{References}
        \begin{thebibliography}{10}
\bibitem{Suehiro88-01J}
N.~Suehiro and M.~Hatori, ``$N$-shift cross-orthogonal sequences,'' {\it IEEE Trans. Info. Theory}, vol. IT-34, no. 1, pp. 143-146, Jan. 1988. 
\bibitem{Suehiro94-06J}
N. Suehiro, ``A signal design without co-channel interference for approximately synchronized CDMA systems," {\it IEEE Journal on Sel. Areas in Commun.}, vol. 12, no. 5, pp. 837-841, June 1994.
\bibitem{Han09-06C}
C. Han and T. Hashimoto, ``$Z$-connecteble complete complementary code and its application in CDMA, in {\it Proc. IEEE Int. Symp. Information Theory} (ISIT2009), June 2009, pp. 438-422.
\bibitem{Han11-09J}
C. Han, N. Suehiro, and T. Hashimoto, `` A systematic framework for the construction of optimal complete complementary codes, {\it IEEE Trans. Information Theory}, vol. 57, no. 9, pp. 6033- 6042, Sept. 2011.
\end{thebibliography}
      \end{block}
    \end{column}
  \end{columns}
\end{frame}
\end{document}